### 2020-01-30 wuhan.tex
pushing figs
Next part of Results

@@

We also evaluate the estimates of $\mathcal R_0$ across different studies by 
replacing the their values of $r$, $\bar G$, and $\kappa$ with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) one at a time and recalculating the basic reproductive number $\mathcal R_0$ (\fref{R0}).
We find that incorporating uncertainties one at a time increases the width of the confidence intervals all but two cases.
We estimate narrower confidence intervals for Study 2 when we use our pooled estimate of the squared CV in generation time $\mu_\kappa$ to recalculate $\mathcal R_0$ because they assume a narrow generation-interval distribution ($\kappa=0$);
when lower values of $\kappa$ are used, their estimates of $\mathcal R_0$ become less sensitive to the values of $r$ and $\bar G$.
We estimate narrower confidence intervals for Study 5 when we use our pooled estimate of the mean generation time $\mu_G$ to recalculate $\mathcal R_0$ because the range of uncertainty in the mean generation time $\bar G$ they consider is much wider than ours (\fref{assumption}).

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{compare_R0.pdf}
\caption{
\textbf{Effect of uncertainties in underlying parameters on the estimate of the basic reproductive number.}
I'm a caption
}
\label{fig:R0}
\end{figure}

When we incorporate all uncertainties by using posterior samples for $\mu_r$, $\mu_G$, and $\mu_\kappa$ to recalculate $\mathcal R_0$ and compare it with the reported $\mathcal R_0$ estimates.
We estimate the average $\mathcal R_0$ to be 3.1 (95\% CI: 2.1--5.7).
While our pooled estimate of $\mathcal R_0$ is similar to other reported values, our calculation gives wider confidence intervals than all of them.
This result does not imply that our assumptions are too weak;
we believe that this confidence interval accurately reflects the level of uncertainties present in the information that were available when these models were fitted.
In fact, our results show that incorporating uncertainties in all parameters can give narrower confidence intervals than doing so one at a time because nonlinear effects of parameters could cancel out and give appropriately wide confidence intervals.

>>>>

\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & $\mathrm{Gamma}(\alpha=28, \beta=28/2.6)$ & constant & constant \\
\hline
Study 2 & $\mathrm{Gamma}(\alpha=67, \beta=67/2.92)$ & constant & constant \\
\hline
Study 3 & N.A. & $\mathrm{Uniform}(6, 10)$ & constant\\
\hline
Study 4 & $\mathrm{Gamma}(\alpha=1400, \beta=1400/3.8)$ & constant & constant \\
\hline
Study 5 & $\mathrm{Gamma}(\alpha=12, \beta=12/2.2)$ & $\mathrm{Uniform}(7, 14)$ & constant\\
\hline
Study 6 & $\mathrm{Gamma}(\alpha=54, \beta=54/5.47)$ & $\mathrm{Uniform}(7.6, 8.4)$ & constant
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions $\mathcal R_0$, $\bar G$, and $\kappa$.}
We use these 
The probability distribution for the exponential growth rate $r$ for each study is obtained by drawing random samples from these distributions and taking the inverse of \eref{gamma}.
The gamma distribution is parameterized by shape $\alpha$ and rate $\beta$ parameters.
Constant distributions assume a fixed values according to Table 1.
}
\end{table}

@@

We also evaluate the estimates of $\mathcal R_0$ across different studies by 
replacing the their values of $r$, $\bar G$, and $\kappa$ with our pooled estimates ($\mu_r$, $\mu_G$, and $\mu_\kappa$) one at a time and recalculating the basic reproductive number $\mathcal R_0$ (\fref{R0}).
We find that incorporating uncertainties one at a time increases the width of the confidence intervals all but two cases.
We estimate narrower confidence intervals for Study 2 when we use our pooled estimate of the squared CV in generation time $\mu_\kappa$ to recalculate $\mathcal R_0$ because they assume a narrow generation-interval distribution ($\kappa=0$);
when lower values of $\kappa$ are used, their estimates of $\mathcal R_0$ become less sensitive to the values of $r$ and $\bar G$. \jd{don't know what this last part means. Doesn't lower kappa mean exactly the opposite? It's what's making the estimate volatile?}
We estimate narrower confidence intervals for Study 5 when we use our pooled estimate of the mean generation time $\mu_G$ to recalculate $\mathcal R_0$ because the range of uncertainty in the mean generation time $\bar G$ they consider is much wider than ours (\fref{assumption}).

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{compare_R0.pdf}
\caption{
\textbf{Effect of uncertainties in underlying parameters on the estimate of the basic reproductive number.}
I'm a caption; \emph{No you're not.}
}
\label{fig:R0}
\end{figure}

When we incorporate all uncertainties by using posterior samples for $\mu_r$, $\mu_G$, and $\mu_\kappa$ to recalculate $\mathcal R_0$ and compare it with the reported $\mathcal R_0$ estimates.
We estimate the average $\mathcal R_0$ to be 3.1 (95\% CI: 2.1--5.7).
While our pooled estimate of $\mathcal R_0$ is similar to other reported values, our calculation gives wider confidence intervals than all of them.
This result does not imply that assumptions based on the pooled estimate are too weak; \jd{better in Discussion?}
we believe that this confidence interval accurately reflects the level of uncertainties present in the information that were available when these models were fitted.
In fact, our results show that incorporating uncertainties in all parameters can give narrower confidence intervals than doing so one at a time because nonlinear effects of parameters could cancel out and give appropriately wide confidence intervals. \jd{Are you sure? I don't think we have a mechanism for cancelling; I think that the narrow GIs cause instability.}
